\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Jaxampler} $\mid$ \emph{\href{https://github.com/Qazalbash/jaxampler}{GitHub}}}{}
\resumeItemListStart
\resumeItem{An opensource JAX-based statistical sampling toolkit.}
\resumeItem{High-Performance Sampling leverage by the power of JAX for high-speed and accuraccy.}
\resumeItem{Provided wide range of sampling methods to suit various applications.}
\resumeItem{Seamlessly integrates with existing JAX workflows.}
\resumeItem{Install using \texttt{pip install --upgrade jaxampler}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Jaxtro} $\mid$ \emph{\href{https://github.com/Qazalbash/jaxtro}{GitHub}}}{}
\resumeItemListStart
\resumeItem{An opensource JAX-based gravitational-wave population inference toolkit.}
\resumeItem{High-Performance Population Inference leverage by the power of JAX for high-speed and accuraccy.}
\resumeItem{Install using \texttt{pip install --upgrade jaxtro}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{GeneTime} $\mid$ \emph{\href{https://github.com/Qazalbash/genetime}{GitHub}}}{}
\resumeItemListStart
\resumeItem{Genetic algorithms based timetable generator.}
\resumeItem{Code not publically available for further refinement and future publication.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Emulated Graphical Pipeline} $\mid$ \emph{\href{https://github.com/Qazalbash/Emulated-Graphical-Pipeline}{GitHub}}}{}
\resumeItemListStart
\resumeItem{Emulated a graphical pipeline in Python.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Processors on Verilog} $\mid$ \emph{\href{https://github.com/Qazalbash/Processors-on-Verilog}{GitHub}}}{}
\resumeItemListStart
\resumeItem{Emulated a RISC-V single cycle processor and 5 staged RISC-V pipelined processor with and without hazard controls in Verilog.}
\resumeItemListEnd



\resumeSubHeadingListEnd
